Icon Generation with Conditional Generative Adversarial Networks

### 2023-01-08 paper/article.tex
footnote -> reference to github repo
missing full stop

    Future work could include testing the performance of cGANs with different hyper-parameters or architectures, or using a different dataset with more balanced class distribution.
    Additionally, exploring the use of cGANs for generating icons with other specific characteristics or properties, such as color or shape, could be a valuable direction for future research

>>>>

    Future work could include testing the performance of cGANs with different hyper-parameters or architectures, or using a different dataset with more balanced class distribution.
    Additionally, exploring the use of cGANs for generating icons with other specific characteristics or properties, such as color or shape, could be a valuable direction for future research.
